---
title       : Sensitity Analysis Call and Put Option
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/highcharts}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(rCharts)
library(dplyr)
library(knitr)

options(RCHART_WIDTH = 1000, RCHART_HEIGHT = 500)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = F)

```

```{r dataPrep, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
data.ttm <- data.frame()
data.vola = data.frame()
data.strike = data.frame()
data.stock = data.frame()
    
# calculate price for different TTM
pctValues <- seq(from = 0.5, to = 1.5, by = 0.05)

strikePrice <- 10
stockPrice <- 10 
vola <- 0.2
ttm <- 1
rf <- 0.05

# for TTM
for(pctValue in pctValues){
  
    #ttm
    x <- pctValue * ttm
    call <- blackscholes(S = stockPrice, X = strikePrice,rf = rf, T = x, sigma = vola)[1]
    put <- blackscholes(S = stockPrice, X = strikePrice,rf = rf, T = x, sigma = vola)[2]
    data.ttm <- rbind(data.ttm, c(x, call , put ))
    
    x <- pctValue * stockPrice
    call <- blackscholes(S = x, X = strikePrice,rf = rf, T = ttm, sigma = vola)[1]
    put <- blackscholes(S = x, X = strikePrice,rf = rf, T = ttm, sigma = vola)[2]
    data.stock <- rbind(data.stock, c(x, call , put ))
    
    x <- pctValue * strikePrice
    call <- blackscholes(S = stockPrice, X = x,rf = rf, T = ttm, sigma = vola)[1]
    put <- blackscholes(S = stockPrice, X = x,rf = rf, T = ttm, sigma = vola)[2]
    data.strike <- rbind(data.strike, c(x, call , put ))
    
    x <- pctValue * vola
    call <- blackscholes(S = stockPrice, X = strikePrice,rf = rf, T = ttm, sigma = x)[1]
    put <- blackscholes(S = stockPrice, X = strikePrice,rf = rf, T = ttm, sigma = x)[2]
    data.vola <- rbind(data.vola , c(x, call , put ))

}

colnames(data.vola) <- c("x", "call", "put")
colnames(data.strike) <- c("x", "call", "put")
colnames(data.stock) <- c("x", "call", "put")
colnames(data.ttm) <- c("x", "call", "put")

drawChart <- function(data, xAxisLabel){
  
    chart <- Highcharts$new()
  chart$chart(type="line")
  chart$title(text="Call and Put Option Pricing")
  chart$yAxis(title = list(text ="Option Price"))
  chart$xAxis(title = list(text =as.character(xAxisLabel)))
  chart$series(name = "Call", data = toJSONArray2(select(data, x, call) %>% arrange(x), json = F, names = F))
  chart$series(name = "Put", data = toJSONArray2(select(data, x, put) %>% arrange(x), json = F, names = F))
  chart$tooltip(shared=T, useHTML=F, crosshairs=T, valueDecimals=4)
  return(chart)
  
}

```


## Introduction

The following slides will give an overview of how option values change if either time to maturity, stock price, strike price or volatility are adjusted, everything else equal.
Generally, the values are set to:
* Strike Price: 10
* Stock Price: 10
* Volatility: 0.20
* Time to Maturity: 1.0
* Interest Rate: 0.05

--- .class #id 

## How Does the Volatility Affect the Option Price?

```{r chartVola, results='asis', echo=FALSE, comment=NA,tidy=FALSE}
drawChart(data.vola, "Volatility")
```

--- .class #id 

## How Does the Strike Price Affect the Option Price?

```{r chartStrike, results='asis', echo=FALSE}

drawChart(data.strike, "Strike Price")

```

--- .class #id 

## How Does the Stock Price Affect the Option Price?

```{r chartStock, results='asis', echo=FALSE}

drawChart(data.stock, "Stock Price")

```

--- .class #id 

## How Does the Time to MaturityAffect the Option Price?

```{r chartTTM, results='asis', echo=FALSE}

drawChart(data.ttm, "Time to Maturity")

```

--- .class #id 

